Formalization, Mechanization and Automation of \\ G\"{o}del's Proof of God's Existence

### 2013-10-31 Talks/FU-Berlin/talk-part-1.tex
several updates for FU talk

* for the existence of god \\

@@

\begin{frame}{Introduction}

\emph{\huge Wohl eine jede Philosophie kreist um den ontologischen
  Gottesbeweis} \\[2em]
(Adorno, Th. W.: Negative Dialektik. Frankfurt a. M. 1966, p.378)
\vfill
\ldots \hfill
\includegraphics[height=2cm]{buch3.jpg} \hfill
\includegraphics[height=2cm]{buch2.jpg} \hfill 
\includegraphics[height=2cm]{buch4.jpg} \hfill
\includegraphics[height=2cm]{buch5.jpg} \hfill
\includegraphics[height=2cm]{buch6.jpg} \hfill
\includegraphics[height=2cm]{buch1.jpg} \hfill
\ldots
\end{frame}

@@

\begin{itemize}
\item[A:] pen and paper: detailed natural deduction proof 
\item[B:] formalization: in classical higher-order logic (\textcolor{blue}{HOL})
\item[] proof automation: theorem provers \textsc{Leo-II} and \textsc{Satallax} 
\item[] consistency: model finder \textsc{Nitpick (Nitrox)} 
\item[C:] step-by-step verification: proof assistant \textsc{Coq} 
\item[D:] automation \& verification: proof assistant 
  \textsc{Isabelle} \\[2em]
%\item[ ] Conclusion \\[2em]
\end{itemize}
Did we get new results? \hfill  \textcolor{red}{Yes --- let's discuss later!}
\end{frame}

>>>>

* for the existence of God \\

@@

\begin{frame}{Introduction}
\vskip1em
\emph{\huge Wohl eine jede Philosophie kreist um den ontologischen
  Gottesbeweis} \\[1.5em]
(Adorno, Th. W.: Negative Dialektik. Frankfurt a. M. 1966, p.378)
\vfill
\begin{center}
\fcolorbox{gray}{white}{
\begin{minipage}{.9\textwidth}
\ldots \hfill
\includegraphics[height=2cm]{buch3.jpg} \hfill
\includegraphics[height=2cm]{buch2.jpg} \hfill 
\includegraphics[height=2cm]{buch4.jpg} \hfill
\includegraphics[height=2cm]{buch5.jpg} \hfill
\includegraphics[height=2cm]{buch6.jpg} \hfill
\includegraphics[height=2cm]{buch1.jpg} \hfill
\ldots
\end{minipage}
}
\end{center}
\end{frame}

@@

\begin{itemize}
\item[A:] Pen and paper: \hfill detailed natural deduction proof 
\item[B:] Formalization: \hfill in classical higher-order logic (\textcolor{blue}{HOL})
\item[] Automation: \hfill theorem provers \textsc{Leo-II} and \textsc{Satallax} 
\item[] Consistency: \hfill model finder \textsc{Nitpick (Nitrox)} 
\item[C:] Step-by-step verification: \hfill proof assistant \textsc{Coq} 
\item[D:] Automation \& verification: \hfill proof assistant \textsc{Isabelle} \\[2em]
%\item[ ] Conclusion \\[2em]
\end{itemize}
Did we get new results? \hfill  \textcolor{red}{Yes --- let's discuss this later!}
\end{frame}
